---
title: "hy2912_p8130_hw1"
author: "Helen Yousaf"
date: "2024-09-19"
output: html_document
---
## Problem I 
## Library Tidyverse

```{r tidyverse, echo=FALSE}
library(tidyverse)
```

## Loading Penguins dataset

```{r df_create}
data("penguins", package = "palmerpenguins")
```

## Describing Penguins Data 
This data presents demographically relevant information for 344 samples of penguins between 2007-2009, including their bill length and depth, flipper length, body mass, and sex. This is organized in a 344 x 8 table and contains `r nrow(penguins)` rows and `r ncol(penguins)` columns. It measures 344 samples and 8 variables. The mean flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)` mm. 

```{r yx_scatter}
ggplot(penguins, aes(x = bill_length_mm,  y = flipper_length_mm, color=species)) + geom_point() 
```
```{r}
ggsave("scatter_plot.pdf", height = 4, width = 6)
```


## Problem 2
```{r}
problem_df = tibble (
  vec_numeric = rnorm(10), 
  char_vec = c("a","b","c","d","e","f","g","h","i","j"),
  fact_vec = factor(sample(c("Level 1", "Level 2", "Level3", 10)))
   ) 
```
