---
title: "hy2912_p8130_hw1"
author: "Helen Yousaf"
date: "2024-09-19"
output: github_document
---
## Problem I 
This is code will evaluate the problem 1 of HW_1.

#### Library Tidyverse
```{r tidyverse, echo=FALSE}
library(tidyverse)
```

#### Loading Penguins dataset
```{r penguin_df_create, echo=TRUE}
data("penguins", package = "palmerpenguins")
```

#### Describing Penguins Data 
This data presents demographically relevant information for 344 samples of penguins between 2007-2009, including their **bill length and depth**, **flipper length**, **body mass**, and **sex**. This is organized in a 344 x 8 table and contains `r nrow(penguins)` rows and `r ncol(penguins)` columns. It measures 344 samples and 8 variables. The **mean** flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)` mm. 

#### Making Scatter Plot
Penguin Bill Length vs. Flipper Length Scatter Plot

This code chunk creates a xy scatterplot of flipper_length_mm (y) vs bill_length_mm (x). Points are colored using the species variable. 
```{r yx_scatter, echo=TRUE, warning=FALSE}
ggplot(penguins, aes(x = bill_length_mm,  y = flipper_length_mm, color=species)) + geom_point() 
```

#### Exporting Scatter Plot
```{r ggsave, echo=TRUE, warning=FALSE}
ggsave("scatter_plot.pdf", height = 4, width = 6)
```

## Problem 2
This section will evaluate problem 2 of HW_1.

#### Creating Dataframe for Problem 2
The chunk below creates a dataframe containing a sample of size 10 from a 
random normal variable, constructs the specified logical vector indicating whether elements are greater than 0. The code chunk also creates a character vector of length 10 and 
a factor vector of length 10, with 3 different factor “levels”. 
```{r, echo = TRUE}
problem_2_df = tibble (
  vec_numeric = rnorm(10), 
  vec_logi = vec_numeric> 0, 
  vec_char = sample (letters, 10),
  vec_fact = factor(sample(c( "Level 1", "Level 2", "Level 3", "Level 1", "Level 2", "Level 3", "Level 1", "Level 2", "Level 3", "Level 1")))
)
```
#### Mean of each variable 
The code chunk finds the mean of each variable in the data frame to determine for which variable it works and doesn’t work.

The mean of vec_numeric is `r mean(pull(problem_2_df, vec_numeric))`.
The mean of vec_logi is `r mean(pull(problem_2_df, vec_logi))`.
The mean of vec_char is `r mean(pull(problem_2_df, vec_char))`.
The mean of vec_fact is `r mean(pull(problem_2_df, vec_fact))`.

Given the qualitative nature of vec_char and vec_fact, determining the mean is not avaialble (NA). These two vectors represent nominal and ordinal categorical variables, respectively and are not numeric or logical. Running the as.numeric() function for these two factors also did not yield an output. 


  
  


