---
title: "hy2912_p8130_hw1"
author: "Helen Yousaf"
date: "2024-09-19"
output: html_document
---
## Problem I 
This is code will evaluate the problem 1 of HW_1.

#### Library Tidyverse
```{r tidyverse, echo=FALSE}
library(tidyverse)
```

#### Loading Penguins dataset
```{r penguin_df_create, echo=TRUE}
data("penguins", package = "palmerpenguins")
```

#### Describing Penguins Data 
This data presents demographically relevant information for 344 samples of penguins between 2007-2009, including their **bill length and depth**, **flipper length**, **body mass**, and **sex**. This is organized in a 344 x 8 table and contains `r nrow(penguins)` rows and `r ncol(penguins)` columns. It measures 344 samples and 8 variables. The **mean** flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)` mm. 

#### Making Scatter Plot
Penguin Bill Length vs. Flipper Length Scatter Plot
```{r yx_scatter, echo=TRUE, warning=FALSE}
ggplot(penguins, aes(x = bill_length_mm,  y = flipper_length_mm, color=species)) + geom_point() 
```
##### Exporting Scatter Plot
```{r ggsave, echo=TRUE, warning=FALSE}
ggsave("scatter_plot.pdf", height = 4, width = 6)
```

## Problem 2
This code will evaluate problem 2 of HW_1.

#### Creating Dataframe for Problem 2
The chunk below creates a dataframe containing a sample of size 10 from a 
random normal variable, constructs the specified logical vector, takes the 
absolute value of each element of that sample,and produces a histogram of 
the absolute value. The code chunk also finds the median of the sample and
stores it for easy in-line printing.
```{r}
problem_df = tibble (
  vec_numeric = rnorm(10), 
  vec_logi = vec_numeric> 0, 
  vec_char = sample (letters, 10),
  vec_fact = factor(sample(c( "Level 1", "Level 2", "Level 3", "Level 1", "Level 2", "Level 3", "Level 1", "Level 2", "Level 3", "Level 1")))
)
```


  
  


